README.md

### 2021-05-16 README.Rmd
github ms 📰
journal issue 🌅

@@

This repository stores all information related to the manuscript *The seed germination spectrum of alpine plants: a global meta-analysis*, including raw data, `R` scripts to process and analyse data, and `Rmarkdown` files to create the manuscript.

@@

* `data` Primary data, including the [germination](https://github.com/efernandezpascual/alpineseeds/blob/master/data/germination.csv) dataset, the species [traits](https://github.com/efernandezpascual/alpineseeds/blob/master/data/traits.csv) and the phylogenetic [tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree.pdf).
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including [MCMCglmm analysis](https://github.com/efernandezpascual/alpineseeds/tree/master/results/MCMCglmm) outputs.
* `src` Scripts in `R` language used to process data and perform the analyses of the manuscript.

@@

Please cite this repository as `The seed germination spectrum of alpine plants: a global meta-analysis. Manuscript in preparation.`

>>>>

[![DOI](https://zenodo.org/badge/254951190.svg)](https://zenodo.org/badge/latestdoi/254951190)

@@

This repository stores all information related to the publication *The seed germination spectrum of alpine plants: a global meta-analysis*, including raw data, `R` scripts to process and analyse data, and `Rmarkdown` files to create the manuscript.

@@

* `data` Primary data, including the [germination](https://github.com/efernandezpascual/alpineseeds/blob/master/data/germination.csv) dataset, the species [traits](https://github.com/efernandezpascual/alpineseeds/blob/master/data/traits.csv) and the phylogenetic [tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree.pdf).
* `doc` Files to create the [manuscript](https://github.com/efernandezpascual/alpineseeds/blob/master/doc/manuscript.md) using `Rmarkdown`.
* `results` Output of the `R` scripts, including [MCMCglmm analysis](https://github.com/efernandezpascual/alpineseeds/tree/master/results/MCMCglmm) outputs.
* `src` Scripts in `R` language used to process data and perform the analyses of the manuscript.

@@

Please cite this repository as:

> Fernández-Pascual E, Carta A, Mondoni A, Cavieres L, Rosbakh S, Venn S, Satyanti A, Guja L, Briceño VF, Vandelook F, Mattana E, Saatkamp A, Bu H, Sommerville K, Poschlod P, Liu K, Nicotra A, Jiménez-Alfaro B (2020) [The seed germination spectrum of alpine plants: a global meta-analysis.](https://doi.org/10.1111/nph.17086) *New Phytologist* 229, 3573-3586.
